Introit

Ecclus. 15: 3, 4; Psalm 104: 1 

He  gave  them  the  water  of  wholesome  
wisdom  to  drink,  alleluia;  and  she  shall  be  
made  strong  in  them,  and  shall  not  be  
moved,  alleluia:  And  she  shall  exalt  them  
forever,  allelúia,  allelúia.  Ps.  Give  glory  to  
the  Lord,  and  call  upon  his  name:  declare  
his deeds among the Gentiles. Glory be to 
the Father. 

AQUA sapiéntiæ potávit eos, allelúia: 
firmábitur  in  illis  et  non  flectétur,  
allelúia:  et  exaltábit  eos  in  ætérnum,  
allelúia, allelúia. Ps. Confitémini Dó-
mino  et  invocáte  nomen  ejus:  an-
nuntiáte   inter   gentes   ópera   ejus.   
Glória Patri. 



GRADUAL 

Psalm 117: 24; 106: 2 

HÆC  dies,   quam   fecit   Dóminus:   
exsultémus  et  lætémur  in  ea.  V.  Di-
cant   nunc,   qui   redémpti   sunt   a   
Dómino:   quos   rédemit   de   manu   
inimíci, et de re
giónibus congregávit 
eos.
 
This is the day which the Lord hath made: 
let  us  be  glad  and  rejoice  therein.  V.    Let  
them  say  so  that  have  been  redeemed  by  
the  Lord,  whom  he  hath  redeemed  from  
the  hand  of  the  enemy:  and  gathered  out  
of the nations. 

ALLELÚIA,    allelúia.    V.    Surrexit    
Dóminus de sepúlcro, qui pro nobis 
pepéndit in ligno. 
Alleluia, alleluia. V. The Lord is risen from 
the  sepulcher,  He,  who  hangeth on the tree.

Offertory

INTÓNUIT  de   coelo   Dóminus,   et   
Altíssimus   dedit   vocem   suam:   et   
apparuérunt  fontes  aquárum,  alleluia.

And the Lord thundered from heaven, and 
the highest gave his voice: Then the foun-
tains of waters appeared, alleluia. 

Communion

SI  consurrexístis  cum  Christo,  quæ  
sursum  sunt  quærite,  ubi  Christus  
est  in  déxtera  Dei  
sedens,  allelúia:  
quæ sursum sunt sápite, allelúia. 

If you be risen with Christ, seek the things 
that  are  above;  where  Christ  is  sitting  at  
the  right  hand  of  God:  alleluia.  Mind  the  
things that are above, alleluia. 

